Empirical study of an algorithm for finding Hamiltonian cycles in 3-regular planar graphs.

### 2024-04-26 paper/main.tex
Add paper

	A Python program of this algorithm is in the appendix \ref{appx:brute-force-count-ham-cyc}.

@@

\subsection{Brute force count Hamiltonian Cycles}\label{appx:brute-force-count-ham-cyc}

>>>>

	A Python program of this algorithm is in the appendix \ref{appx:count-hamcyc-brute-force}.

@@

\subsection{Count Hamiltonian Cycles with Brute Force}
\label{appx:count-hamcyc-brute-force}
\pyfile{count_hamcyc_brute_force.py}
